---
title: ''
author: ''
date: ''
output:
  pdf_document: null
  fig_crop: no
  html_document:
    df_print: paged
subtitle: ''
highlight: tango
number_sections: no
fig_caption: yes
keep_tex: yes
includes:
  in_header: Estilo.sty
classoption: a4paper
always_allow_html: yes
---

\begin{center}
{\Large
  DEPARTAMENTO DE ESTATÍSTICA} \\[0.5cm]
\begin{figure}[!t]
\centering
\includegraphics[width=9cm, keepaspectratio]{logo-UnB.eps}
\end{figure}
{\large
  `r format(Sys.time(), '%d %B %Y')`} \\[0.5cm]
{\LARGE
  \textbf{Atividade 2}} \\[0.5cm]
{\Large
  Prof. Maria Tereza Leão Costa} \\[0.5cm]
{\Large
  Aluno: Bruno Gondim Toledo} \\[0.5cm]
{\Large
  Matrícula: 15/0167636} \\[0.5cm]
{\Large
  Análise de Dados Categorizados} \\[0.5cm]
{\Large
  1º/2024} \\[0.5cm]
\end{center}
\newpage

```{r setup, include=F}
source("source/source.R")
p_load(exact2x2)
```

```{r}
options(scipen=999)
a = 12
b = 0
c = 0
d = 6

(factorial(a+b) * factorial(c+d) * factorial(a+c) * factorial(b+d))/
(factorial(a) * factorial(b) * factorial(c) * factorial(d) * factorial(a+b+c+d))

```

```{r}

t3 = matrix(c(8,4,4,2),2,2)
fisher.test(t3, alternative = "greater")

t4 = matrix(c(9,3,3,3),2,2)
fisher.test(t4, alternative = "greater")

t5 = matrix(c(10,2,2,4),2,2)
fisher.test(t5, alternative = "greater")

t2 = matrix(c(7,5,5,1),2,2)
fisher.test(t2, alternative = "greater")

t1 = matrix(c(6,6,6,0),2,2)
fisher.test(t1, alternative = "greater")

t6 = matrix(c(11,1,1,5),2,2)
fisher.test(t6, alternative = "greater")

t7 = matrix(c(12,0,0,6),2,2)
fisher.test(t7, alternative = "greater")

```

```{r}
t3 = matrix(c(8,4,4,2),2,2)
chisq.test(t3, correct = F)

t4 = matrix(c(9,3,3,3),2,2)
chisq.test(t4, correct = F)

t5 = matrix(c(10,2,2,4),2,2)
chisq.test(t5, correct = F)

t2 = matrix(c(7,5,5,1),2,2)
chisq.test(t2, correct = F)

t1 = matrix(c(6,6,6,0),2,2)
chisq.test(t1, correct = F)

t6 = matrix(c(11,1,1,5),2,2)
chisq.test(t6, correct = F)

t7 = matrix(c(12,0,0,6),2,2)
chisq.test(t7, correct = F)
```

```{r}

t3 = matrix(c(8,4,4,2),2,2)
fisher.exact(t3, midp=T)


t4 = matrix(c(9,3,3,3),2,2)
fisher.exact(t4, midp=T)


t5 = matrix(c(10,2,2,4),2,2)
fisher.exact(t5, midp=T)


t2 = matrix(c(7,5,5,1),2,2)
fisher.exact(t2, midp=T)


t1 = matrix(c(6,6,6,0),2,2)
fisher.exact(t1, midp=T)


t6 = matrix(c(11,1,1,5),2,2)
fisher.exact(t6, midp=T)


t7 = matrix(c(12,0,0,6),2,2)
fisher.exact(t7, midp=T)
```


```{r}

t3 = matrix(c(8,4,4,2),2,2)
fisher.exact(t3, midp=T, alternative = "greater")


t4 = matrix(c(9,3,3,3),2,2)
fisher.exact(t4, midp=T, alternative = "greater")


t5 = matrix(c(10,2,2,4),2,2)
fisher.exact(t5, midp=T, alternative = "greater")


t2 = matrix(c(7,5,5,1),2,2)
fisher.exact(t2, midp=T, alternative = "greater")


t1 = matrix(c(6,6,6,0),2,2)
fisher.exact(t1, midp=T, alternative = "greater")


t6 = matrix(c(11,1,1,5),2,2)
fisher.exact(t6, midp=T, alternative = "greater")


t7 = matrix(c(12,0,0,6),2,2)
fisher.exact(t7, midp=T, alternative = "greater")
```


